RVD2: An ultra-sensitive variant detection model for low-depth targeted next-generation sequencing data

### 2014-01-07 doc/bioinformatics2014/document.tex
Add the command line citation in to the manuscript

Increasingly, NGS is being used to interrogate mutations in heterogeneous clinical samples. For example, NGS-based non-invasive fetal DNA testing uses maternal blood sample to sequence the minority fraction of cell-free fetal DNA~\citep{Fan:2008di}. Infectious diseases such as HIV and influenza may contain many genetically heterogeneous sub-populations~\citep{Flaherty:2011ja, Ghedin:2010ie}. DNA sequencing of individual regions of a solid tumor has revealed genetic heterogeneous within an individual sample~\citep{Navin:2010gu}.

>>>>

Increasingly, NGS is being used to interrogate mutations in heterogeneous clinical samples. For example, NGS-based non-invasive fetal DNA testing uses maternal blood sample to sequence the minority fraction of cell-free fetal DNA~\citep{Fan:2008di}. Infectious diseases such as HIV and influenza may contain many genetically heterogeneous sub-populations~\citep{Flaherty:2011ja,cushing2013rvd, Ghedin:2010ie}. DNA sequencing of individual regions of a solid tumor has revealed genetic heterogeneous within an individual sample~\citep{Navin:2010gu}.
